From Active Hostilities to Frozen Stalemates: Assessing the Role of External Support in Civil Conflict Dynamics

### 2023-10-31 paper.qmd
Avoid kable for docx output support

[//]: # Setup R environment
```{r setup, include = F}
library(dplyr)
library(ggplot2)
library(ggthemes)
library(ggdist)
library(modelsummary)
library(kableExtra)
library(knitr)
library(patchwork)
library(tidyr)

@@

fits <- lapply(models, \(dir) file.path(dir, "fit.rds") |> readRDS())

frozen <- fits[grepl("/frozen", models)]
strict_frozen <- fits[grepl("/strict_frozen", models)]

modelsummary(frozen, pars = c("alpha", "delta", "beta"),
             statistic = "conf.int", title = "Frozen Conflicts") |>
    add_header_above(c(" " = 1, "All Episodes" = 3, "High Intensity Only" = 3)) |>
    kable_styling(font_size = 8, full_width = F) |>
    landscape()
```

```{R}
modelsummary(strict_frozen, pars = c("alpha", "delta", "beta"),
             statistic = "conf.int", title = "Frozen Conflicts Lasting >2 Years") |>
    add_header_above(c(" " = 1, "All Episodes" = 3, "High Intensity Only" = 3)) |>
    kable_styling(font_size = 8, full_width = F) |>
    landscape()
```

>>>>

[//]: # Setup R environment
```{r setup, include = F}
library(dplyr)
library(ggplot2)
library(ggthemes)
library(ggdist)
library(modelsummary)
library(knitr)
library(patchwork)
library(tidyr)

@@

```{R}
regtable <- function(fits, ...) {
    names(fits) <- NULL
    modelsummary(fits, pars = c("delta", "beta", "alpha"), statistic = "conf.int", ...)
}

m <- c("frozen-bin-all", "strict_frozen-bin-all",
       "frozen-bin-high_intensity", "strict_frozen-bin-high_intensity")
regtable(fits[m], title = "Binary Treatments")
```

```{R}
m <- c("frozen-bin_5y-all", "strict_frozen-bin_5y-all",
       "frozen-bin_5y-high_intensity", "strict_frozen-bin_5y-high_intensity")
regtable(fits[m], title = "Binary Treatments - Last 5 Years")
```

```{R}
m <- c("frozen-prop-all", "strict_frozen-prop-all",
       "frozen-prop-high_intensity", "strict_frozen-prop-high_intensity")
regtable(fits[m], title = "Proportion Treatments")
```
